Artistic Curve Steganography Carried by Musical Audio

### 2022-11-13 writeup/paper.tex
Mostly finished writing about frame misalignments

\begin{equation}
  S_{k, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k, j} \left( e^{i P_{k, j}} \right)
\end{equation}

@@

\begin{equation}
  \text{SWS}_{\ell}\left({M_k}\right)_j = \sum_{n = 0}^{\ell-1} M_{k, j+n}
\end{equation}

@@

\begin{equation}
  \label{eq:objfn}
  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
\end{equation}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{WindowEffect.pdf}
  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$.  A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large can over-smooth.}
  \label{fig:WindowEffect}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$.  A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
  \label{fig:LambdaEffect}
\end{figure}

subject to $\hat{M_{k, j}} \geq 0$.  In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible, while preserving the original audio as well as possible, according to $\lambda$.  A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.  Figure~\ref{fig:LambdaEffect} shows an example of varying $\lambda$.

\subsubsection{Computational Complexity}
\label{sec:computation}
Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms for solving such systems efficiently via repeated evaluation of the linear system and its adjoint.  Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, the linear operator and its adjoint can be implemented with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.  For example, let

\begin{equation}
  \label{eq:cumusum}
  C_{k, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
\end{equation}

then Equation~\ref{eq:objfn} can be rewritten as 
\begin{equation}
  \label{eq:objfncumusum}
  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k, j+\ell}-C_{k, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
\end{equation}

@@

In general, the SWS-STFT sequence $X$ will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{OptimalShift.pdf}
  \caption{Curve length can be used as a proxy for distortion.}
  \label{fig:TSPTour}
\end{figure}

>>>>

\begin{equation}
  S_{k_i, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k_i, j} \left( e^{i P_{k_i, j}} \right)
\end{equation}

@@

\begin{equation}
  \text{SWS}_{\ell}\left({M_k}\right)_j = \sum_{n = 0}^{\ell-1} M_{k_i, j+n}
\end{equation}

@@

\begin{equation}
  \label{eq:objfn}
  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
\end{equation}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{WindowEffect.pdf}
  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$, using the lowest two non-DC frequencies to embed each coordinate.  A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large can over-smooth.}
  \label{fig:WindowEffect}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$, embedding using the lowest two non-DC frequencies to.  A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
  \label{fig:LambdaEffect}
\end{figure}

subject to $\hat{M_{k_i, j}} \geq 0$.  In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible, while preserving the original audio as well as possible, according to $\lambda$.  A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.  Figure~\ref{fig:LambdaEffect} shows an example of varying $\lambda$.

After solving for $\hat{M_{k_i, j}}$, we replace all rows of $M_{k_i}$ with $\hat{M_{k_i}}$, and we perform an inverse STFT of $M e^{i P}$ for the original phases $P$ (Section~\ref{sec:componentscales} will explain when it is necessary to modify the phases as well).  We can then save the resulting audio in a compressed format, and recover the hidden signal by loading it in and extracting the corresponding components of the magnitude SW-STFT.

\subsubsection{Computational Complexity}
\label{sec:computation}
Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms \cite{branch1999subspace} for solving such systems efficiently via repeated evaluation of the linear system and its adjoint on iterative estimates of a solution .  Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, the linear operator and its adjoint can be implemented with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.  For example, let

\begin{equation}
  \label{eq:cumusum}
  C_{k_i, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
\end{equation}

then Equation~\ref{eq:objfn} can be rewritten as 
\begin{equation}
  \label{eq:objfncumusum}
  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k_i, j+\ell}-C_{k_i, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
\end{equation}

@@

In general, the SWS-STFT sequence will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{OptimalShift.pdf}
  \caption{Curve length can be used as a proxy for distortion, so a shift which minimizes curve length is most likely the shift needed to re-align audio to frame windows.  The dot here indicates the ground truth shift of an embedding using the lowest two non-DC frequencies with $\lambda=0.1, \ell=16$, and the global mins exactly match ground truth.}
  \label{fig:FrameAlignments}
\end{figure}

What we've described so far works for audio that's aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.  To this end, we can use the fact that the curves don't jump very far from sample to sample; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.  Therefore, if the embedding is frame aligned, the length of the curve should be minimized.  Conversely, if the embedding is not frame aligned, the curve becomes noisy and is more likely to jump around quickly from sample to sample.  Figure~\ref{fig:FrameAlignments}
